---
title: "Reading Bruker OPUS binary files in R"
author: "Philipp Baumann"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{Reading Bruker OPUS binary files in R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Bruker instruments produce a proprietary file format when measuring spectra. This way the Bruker OPUS software stores all measurement
parameters, configurations, environmental conditions, for different spectral data types as OPUS binary files.

Our package can read thosee binary files for most of the
Fourier-Transform(FT)-Infrared(IR)-spectrometers from Bruker Optics GmBH.

# Reading many OPUS files

```{r}
library("opusreader2")
file <- opus_file()
data_list <- read_opus(file)
```

`read_opus` is a list-parser using S3 classes. The data is arranged
as shown in the Bruker OPUS viewer:

```{r}
names(data_list)
```
