---
title: "Reading Bruker OPUS binary files in R"
author: "Philipp Baumann"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{Reading Bruker OPUS binary files in R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Bruker instruments produce a proprietary file format to store all measurement
parameters, configurations, environmental conditions, and spectral data types
saved. The Bruker OPUS software does the measurements and produces thhe 
OPUS binary files.

Our package can read thosee binary files for most of the
Fourier-Transform(FT)-Infrared(IR)-spectrometers from Bruker Optics GmBH.

# Reading many OPUS files

## Basic usage

```{r}
library("opusreader2")
file <- opus_file()
data_list <- read_opus(file)
```

`read_opus` is a list-parser using S3 classes. The data is arranged
as shown in the Bruker OPUS viewer:

```{r}
names(data_list)
```
